% ============================================================
%  Hwan Ji — Academic CV
%  Compile: pdflatex Hwan_Ji_CV.tex   (or upload to Overleaf)
% ============================================================
\documentclass[10pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.8cm, bottom=1.8cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{lmodern}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\definecolor{muted}{RGB}{100,100,100}

% ── Section header ──────────────────────────────────────────
\newcommand{\cvsec}[1]{%
  \vspace{0.9em}%
  \noindent{\small\bfseries\MakeUppercase{#1}}%
  \vspace{0.15em}\newline%
  \noindent\rule{\linewidth}{0.4pt}%
  \vspace{0.4em}%
}

% ── Column widths ───────────────────────────────────────────
\newlength{\datecol}  \setlength{\datecol}{2.9cm}
\newlength{\maincol}  \setlength{\maincol}{\dimexpr\linewidth-\datecol-0.3cm}

% ── Two-column entry (minipage prevents column bleed) ───────
%    #1 date  #2 content (use \\ freely inside)
\newcommand{\cvrow}[2]{%
  \noindent
  \begin{tabular}{@{}p{\datecol}@{\hspace{0.3cm}}p{\maincol}@{}}
    {\footnotesize\color{muted}\raggedright #1} &
    \begin{minipage}[t]{\maincol}#2\end{minipage}
  \end{tabular}\\[0.5em]%
}

% ── Inline skill row ────────────────────────────────────────
\newcommand{\skillrow}[2]{%
  \noindent
  \begin{tabular}{@{}p{\datecol}@{\hspace{0.3cm}}p{\maincol}@{}}
    {\footnotesize\color{muted}#1} & {\small #2}
  \end{tabular}\\[0.3em]%
}

% ============================================================
\begin{document}

% ── Header ──────────────────────────────────────────────────
\begin{center}
  {\Large\textbf{Hwan Ji}}\\[0.35em]
  {\small
    Seoul National University $\cdot$ Seoul, Republic of Korea\\[0.15em]
    \href{mailto:saturdayynightlive@snu.ac.kr}{saturdayynightlive@snu.ac.kr}
    $\;\cdot\;$
    \href{https://github.com/saturdayynightlive}{github.com/saturdayynightlive}
    $\;\cdot\;$
    \href{https://saturdayynightlive.github.io}{saturdayynightlive.github.io}
  }
\end{center}

% ── Education ───────────────────────────────────────────────
\cvsec{Education}

\cvrow{Mar.~2025\,--\,Feb.~2029}{%
  \textbf{Seoul National University}, Seoul, S.Korea\\[0.1em]
  {\small B.S.\ in Computer Science \& Engineering}\\
  {\small Minor in Statistics (from Sep.~2026)}\\
  {\small College of Liberal Studies}%
}

% ── Research Interests ──────────────────────────────────────
\cvsec{Research Interests}

\noindent{\small Broadly interested in artificial intelligence and machine learning research.}

% ── Projects ────────────────────────────────────────────────
\cvsec{Projects}

\cvrow{2024}{%
  \textbf{Evening Self-Study Request System}\\[0.1em]
  {\small Node.js $\cdot$ Swift (iPad) $\cdot$ MySQL}\\[0.2em]
  \begin{itemize}[nosep, leftmargin=1em, topsep=3pt, itemsep=1pt]
    \item[\small$\bullet$] {\small Collaborated with a peer (responsible for app UI design) to digitize the paper-based evening self-study movement request process at a high school.}
    \item[\small$\bullet$] {\small Developed the backend and chose Swift/iPad as the client platform because the school provided iPads to all students at no cost, ensuring universal access without requiring personal devices.}
    \item[\small$\bullet$] {\small Completed a pilot; full deployment was deferred due to institutional data-protection requirements for student personal records.}
  \end{itemize}%
}

\cvrow{2023}{%
  \textbf{Green City Planner} --- High School Research Program\\[0.1em]
  {\small visionOS}\\[0.2em]
  \begin{itemize}[nosep, leftmargin=1em, topsep=3pt, itemsep=1pt]
    \item[\small$\bullet$] {\small Built a visionOS application for interactive 3D urban design, aimed at streamlining environmental impact assessments.}
    \item[\small$\bullet$] {\small Collaborated with a peer (responsible for overall UI); led all technical aspects including asset preparation, scene layout, and environmental scoring.}
  \end{itemize}%
}

\cvrow{2022}{%
  \textbf{Optimal Transit Route Distribution via Machine Learning}\\[0.1em]
  {\small R $\cdot$ Logistic Regression}\\[0.2em]
  \begin{itemize}[nosep, leftmargin=1em, topsep=3pt, itemsep=1pt]
    \item[\small$\bullet$] {\small Explored correlations between municipal indicators (population, income, bus stops) and tram/subway route placement in Daejeon; built a logistic regression model to predict optimal station distribution.}
    \item[\small$\bullet$] {\small Led all technical aspects: data collection, preprocessing, visualization, and model training.}
  \end{itemize}%
}

% ── Relevant Coursework ─────────────────────────────────────
\cvsec{Relevant Coursework}

\noindent{\small
  Statistics\;(A$^{+}$),\enspace
  Statistics Lab.\;(A$^{+}$),\enspace
  Discrete Mathematics,\enspace
  Engineering Mathematics,\enspace
  Computing Core: Data-Centered AI,\enspace
  Computer Programming,\enspace
  Logic Design%
}

% ── Honors & Awards ─────────────────────────────────────────
\cvsec{Honors \& Awards}

\cvrow{Mar.~2026}{%
  \textbf{Silla Foundation Scholarship} --- Full-Tuition for 3 Years\\
  {\small Silla Cultural Scholarship Foundation, Seoul, S.Korea}\\
  {\small Competitive merit-based external scholarship; full tuition for three years.}%
}

\cvrow{Feb.~2026}{%
  \textbf{SNU Customized Scholarship} --- Tuition Exemption\\
  {\small Seoul National University, Seoul, S.Korea}\\
  {\small Merit-based internal scholarship awarded to selected students.}%
}

\cvrow{Aug.~2025}{%
  \textbf{Donggok Lee Yong-hee Scholarship} --- Full-Tuition\\
  {\small Donggok Lee Yong-hee Foundation, Seoul, S.Korea}\\
  {\small Competitive external scholarship covering full tuition.}%
}

% ── Skills ──────────────────────────────────────────────────
\cvsec{Skills}

\skillrow{Programming}{Python,\enspace C,\enspace C\texttt{++},\enspace Java,\enspace Swift,\enspace R}
\skillrow{Tools}{Git,\enspace Linux;\enspace PyTorch\,(learning)}
\skillrow{Languages}{Korean\,(Native),\enspace English\,(Fluent --- TEPS\;444)}

% ── Teaching ────────────────────────────────────────────────
\cvsec{Teaching}

\cvrow{Mar.\,--\,Jun.~2026}{%
  \textbf{Undergraduate Mentor}\\
  {\small Freshman Seminar: ``A Journey to Safe Research'', Seoul National University}
  \begin{itemize}[nosep, leftmargin=1em, topsep=3pt, itemsep=1pt]
    \item[\small$\bullet$] {\small Supervised class activities and provided individual academic guidance for first-year students.}
    \item[\small$\bullet$] {\small Facilitated discussions on laboratory safety protocols and collaborative research practices.}
  \end{itemize}%
}

% ── Extracurricular ─────────────────────────────────────────
\cvsec{Extracurricular}

\cvrow{Jul.\,--\,Aug.~2025}{%
  \textbf{Student Mentor}\\
  {\small SAM (SNU Active Mentoring), College of Education}\\
  {\small Mentored local middle school students in Mathematics and Science;
  developed individualized study plans and facilitated goal-setting sessions.}\\
  {\small Awarded \textbf{Outstanding Mentor of the Semester}.}%
}

% ── Footer ──────────────────────────────────────────────────
\vfill
\noindent{\footnotesize\color{muted}Updated: May 14, 2026}

\end{document}
