\documentclass[11pt,a4paper]{article}

% ===== XeLaTeX + Korean =====
\usepackage{kotex}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\setmainhangulfont{AppleMyungjo}
\setsanshangulfont{Apple SD Gothic Neo}

% ===== Layout =====
\usepackage[a4paper,top=18mm,bottom=18mm,left=20mm,right=20mm]{geometry}
\usepackage{fancyhdr}
\setlength{\headheight}{24pt}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{array}

\setlength{\parindent}{1em}
\linespread{1.18}

% ===== Header / Footer =====
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.6pt}
\fancyhead[L]{\sffamily\bfseries 2026 고1 영어 변형 — 지문 28}
\fancyhead[R]{\sffamily Food Truck Festival 안내문}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\framebox[16mm][c]{\thepage}}

% ===== helpers =====
\newcommand{\qno}[1]{\par\vspace{8pt}\noindent{\sffamily\bfseries #1.}\ }
\newcommand{\instr}[1]{{\sffamily #1}\par\vspace{3pt}}
\newlist{choices}{enumerate}{1}
\setlist[choices]{label=,leftmargin=1.5em,itemsep=2pt,topsep=3pt,parsep=0pt}

\newmdenv[linewidth=0.6pt,roundcorner=3pt,innertopmargin=7pt,innerbottommargin=7pt,
          innerleftmargin=9pt,innerrightmargin=9pt,skipabove=5pt,skipbelow=5pt]{pbox}
\newcommand{\nemo}[1]{\fbox{\,#1\,}}

\begin{document}

\begin{center}
{\fontsize{15}{17}\selectfont\sffamily\bfseries [지문 28] 다음 글을 읽고 물음에 답하시오.}
\end{center}
\vspace{4pt}

% ===== 공통 지문 =====
\begin{pbox}
\begin{center}
{\sffamily\bfseries Food Truck Festival}
\end{center}
Come hungry and leave happy! Join our annual food truck festival with over 20 trucks.\par
\vspace{6pt}
{\sffamily\bfseries When \& Where}\par
\hspace{1em}$\bullet$ August 16, from 11 a.m.\ to 9 p.m.\par
\hspace{1em}$\bullet$ Emton Park\par
\vspace{6pt}
{\sffamily\bfseries Festival Highlights}\par
\hspace{1em}$\bullet$ Free sample tastings between 2 p.m.\ and 3 p.m.\par
\hspace{1em}$\bullet$ Live music performances throughout the festival\par
\hspace{1em}$\bullet$ Cookie-making classes for children\par
\vspace{6pt}
{\sffamily\bfseries Notes}\par
\hspace{1em}$\bullet$ There is no entry fee.\par
\hspace{1em}$\bullet$ Parking is available for free.\par
\vspace{4pt}
\noindent\hspace{1em}{\small ※ For the full schedule, visit \texttt{www.emtontruckfest.com}.}
\end{pbox}

% ===================== Q1 =====================
\qno{1}\instr{윗글의 내용과 일치하지 \underline{않는} 것은?}
\begin{choices}
\item ① This food truck gathering takes place on a yearly basis.
\item ② Visitors may enjoy musical entertainment at any point during the festival.
\item ③ Free food samples are available to taste for the entire duration of the event.
\item ④ Attendees do not need to pay anything to enter the festival grounds.
\item ⑤ A hands-on activity is provided specifically for younger visitors.
\end{choices}

% ===================== Q2 (서술형) =====================
\qno{2}\instr{[서술형] 다음 물음에 답하시오.}
\vspace{2pt}\par\noindent
(1) 주차 비용에 대해 안내문이 언급한 내용을 우리말로 쓰시오.
\par\vspace{4pt}\noindent
$\Rightarrow$ \rule{10cm}{0.4pt}
\vspace{10pt}\par\noindent
(2) 무료 시식(free sample tastings)이 제공되는 시간대를 영어로 쓰시오.
\par\vspace{4pt}\noindent
$\Rightarrow$ \rule{10cm}{0.4pt}

% ===================== Q3 =====================
\qno{3}\instr{윗글의 목적으로 가장 적절한 것은?}
\begin{choices}
\item ① to ask visitors to volunteer at a park cleanup event
\item ② to introduce a food truck festival and its main attractions
\item ③ to announce the cancellation of a public food event
\item ④ to compare different food trucks by price and popularity
\item ⑤ to recruit children for a professional cooking contest
\end{choices}

% ===================== Q4 =====================
\qno{4}\instr{[서술형] 축제는 총 몇 시간 동안 진행되는지 숫자로 쓰시오.}
\par\vspace{4pt}\noindent
$\Rightarrow$ \rule{4cm}{0.4pt}

\end{document}
