\documentclass[11pt,a4paper]{article}

\usepackage{kotex}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\setmainhangulfont{AppleMyungjo}
\setsanshangulfont{Apple SD Gothic Neo}

\usepackage[a4paper,top=18mm,bottom=18mm,left=20mm,right=20mm]{geometry}
\usepackage{fancyhdr}
\setlength{\headheight}{24pt}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{array}
\usepackage{booktabs}

\setlength{\parindent}{1em}
\linespread{1.18}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.6pt}
\fancyhead[L]{\sffamily\bfseries 2026 고1 영어 변형 — 지문 25}
\fancyhead[R]{\sffamily [자율주행차 신뢰도 도표]}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\framebox[16mm][c]{\thepage}}

\newcommand{\qno}[1]{\par\vspace{8pt}\noindent{\sffamily\bfseries #1.}\ }
\newcommand{\instr}[1]{{\sffamily #1}\par\vspace{3pt}}
\newlist{choices}{enumerate}{1}
\setlist[choices]{label=,leftmargin=1.5em,itemsep=2pt,topsep=3pt,parsep=0pt}
\newmdenv[linewidth=0.6pt,roundcorner=3pt,innertopmargin=7pt,innerbottommargin=7pt,
          innerleftmargin=9pt,innerrightmargin=9pt,skipabove=5pt,skipbelow=5pt]{pbox}
\newcommand{\nemo}[1]{\fbox{\,#1\,}}

\begin{document}

\begin{center}
{\fontsize{15}{17}\selectfont\sffamily\bfseries [지문 25] 다음 표와 글을 읽고 물음에 답하시오.}
\end{center}
\vspace{4pt}

\begin{center}
{\bfseries The Extent of People's Trust in Self-Driving Cars, 2023}
\end{center}
\vspace{2pt}

\begin{center}
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
 & \textbf{A great deal} & \textbf{A lot} & \textbf{A little} & \textbf{Not at all} \\\hline
U.K.   & 4\%  & 10\% & 34\% & 52\% \\\hline
U.S.   & 6\%  & 13\% & 30\% & 51\% \\\hline
China  & 8\%  & 47\% & 35\% & 10\% \\\hline
India  & 22\% & 29\% & 35\% & 14\% \\\hline
\end{tabular}
\end{center}
\par\noindent\small\textit{Note: Over 1,000 respondents surveyed per selected country}

\vspace{6pt}

\noindent The graph above shows the extent of people's trust in self-driving cars based on a survey in 2023. ① All countries except India had less than 10\% of people who trusted self-driving cars a great deal. ② More than half of the people in the U.K.\ and the U.S.\ did not trust self-driving cars at all. ③ China was the only country where the percentage of people who trusted self-driving cars a lot was over 40\%. ④ China and India had the same percentage of people who trusted self-driving cars a little. ⑤ In India, the percentage of people who did not trust self-driving cars at all was the lowest among the four countries.

\vspace{10pt}

% Q1
\qno{1}\instr{다음 표의 내용과 일치하지 \textbf{않는} 것은?}
\begin{choices}
\item ① Among the four countries, only India had 20\% or more respondents with the highest level of trust.
\item ② In the U.K.\ and the U.S., more than half of respondents placed in the lowest trust category.
\item ③ China was the sole country where more than 40\% of respondents chose ``a lot'' of trust.
\item ④ All four countries showed the same percentage in the ``a little'' trust category.
\item ⑤ China recorded the lowest share of respondents who expressed no trust in self-driving cars at all.
\end{choices}

\vspace{14pt}

% Q2
\qno{2}\instr{[서술형] 표를 참고하여 다음 물음에 답하시오.}

\noindent (1) China에서 자율주행차를 ``A lot'' 또는 ``A great deal'' 신뢰한다고 응답한 비율의 합을 쓰시오.

\noindent $\Rightarrow$ \rule{4cm}{0.4pt}

\vspace{10pt}

\noindent (2) 네 나라 중 ``A great deal''과 ``A lot''을 합산한 신뢰 비율이 가장 높은 나라를 쓰시오.

\noindent $\Rightarrow$ \rule{4cm}{0.4pt}

% ===================== Q3 =====================
\qno{3}\instr{``A great deal''과 ``A lot''을 합산했을 때, 두 번째로 높은 신뢰 비율을 보인 나라는?}
\begin{choices}
\item ① U.K.
\item ② U.S.
\item ③ China
\item ④ India
\item ⑤ China and India
\end{choices}

% ===================== Q4 =====================
\qno{4}\instr{[서술형] U.K.에서 ``Not at all'' 응답 비율은 ``A great deal'' 응답 비율보다 몇 퍼센트포인트 높은지 쓰시오.}
\par\vspace{4pt}\noindent
$\Rightarrow$ \rule{4cm}{0.4pt}

\end{document}
