\documentclass[11pt,a4paper]{article}

% ===== XeLaTeX + Korean =====
\usepackage{kotex}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\setmainhangulfont{AppleMyungjo}
\setsanshangulfont{Apple SD Gothic Neo}

% ===== Layout =====
\usepackage[a4paper,top=18mm,bottom=18mm,left=20mm,right=20mm]{geometry}
\usepackage{fancyhdr}
\setlength{\headheight}{24pt}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{array}
\usepackage{booktabs}

\setlength{\parindent}{1em}
\linespread{1.18}

% ===== Header / Footer =====
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.6pt}
\fancyhead[L]{\sffamily\bfseries 2026 고1 영어 변형 — 지문 39}
\fancyhead[R]{\sffamily 삼림 파괴와 탄소 순환}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\framebox[16mm][c]{\thepage}}

% ===== helpers =====
\newcommand{\qno}[1]{\par\vspace{8pt}\noindent{\sffamily\bfseries #1.}\ }
\newcommand{\instr}[1]{{\sffamily #1}\par\vspace{3pt}}
\newlist{choices}{enumerate}{1}
\setlist[choices]{label=,leftmargin=1.5em,itemsep=2pt,topsep=3pt,parsep=0pt}
\newmdenv[linewidth=0.6pt,roundcorner=3pt,innertopmargin=7pt,innerbottommargin=7pt,
          innerleftmargin=9pt,innerrightmargin=9pt,skipabove=5pt,skipbelow=5pt]{pbox}
\newcommand{\nemo}[1]{\fbox{\,#1\,}}

\begin{document}

\begin{center}
{\fontsize{15}{17}\selectfont\sffamily\bfseries [지문 39] 다음 글을 읽고 물음에 답하시오.}
\end{center}
\vspace{4pt}

% ===== 삽입 문장 박스 =====
\begin{pbox}
\noindent\textit{In fact, a single mature tree can absorb more than 20 kilograms of CO2 per year,
making forests one of the most powerful tools against climate change.}
\end{pbox}

\vspace{4pt}

% ===== 공통 지문 =====
\begin{pbox}
Approximately 15--20\% of global greenhouse gas emissions are caused by
degradation* and deforestation. Trees play a huge role in the carbon cycle.
( ① ) They convert the CO2 in the air to oxygen through the process of
photosynthesis**, and consequently, they are viewed as a natural regulator of
carbon dioxide. ( ② ) The existence of a larger amount of trees will no doubt
lead to the reduced presence of carbon dioxide in the atmosphere and the
increased existence of oxygen. ( ③ ) And with half of the Earth's forests gone,
the amount of carbon dioxide is progressively rising. ( ④ ) With more carbon
dioxide in the atmosphere, more of the sun's radiation*** is being reflected back
to Earth instead of being released into space, and this is causing the planet's
average temperature to rise. ( ⑤ ) Accordingly, deforestation is a major issue
when it comes to global warming.

\medskip
\footnotesize
* degradation: (환경) 악화\quad
** photosynthesis: 광합성\quad
*** radiation: 복사 (에너지)
\end{pbox}

% ===================== Q1 =====================
\qno{1}\instr{글의 흐름으로 보아, 주어진 문장이 들어가기에 가장 적절한 곳을 고르시오. [3점]}
\begin{choices}
\item ① \quad ② \quad ③ \quad ④ \quad ⑤
\end{choices}

% ===================== Q2 =====================
\qno{2}\instr{다음은 윗글을 요약한 것이다. 빈칸 (A), (B)에 들어갈 말로 가장 적절한 것은?}

\begin{quote}
\itshape
Trees play a crucial role in \underline{\quad(A)\quad} carbon dioxide from the
atmosphere, but deforestation has \underline{\quad(B)\quad} this natural process,
leading to rising CO2 levels and global warming.
\end{quote}

\vspace{4pt}
\noindent
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{clcl}
\toprule
 & \multicolumn{1}{c}{\sffamily (A)} & & \multicolumn{1}{c}{\sffamily (B)} \\
\midrule
① & producing & & accelerated \\
② & producing & & restored    \\
③ & removing  & & disrupted   \\
④ & removing  & & reinforced  \\
⑤ & storing   & & improved    \\
\bottomrule
\end{tabular}

% ===================== Q3 =====================
\qno{3}\instr{윗글의 제목으로 가장 적절한 것은?}
\begin{choices}
\item ① Forests, Carbon Regulation, and the Warming Cost of Deforestation
\item ② Why Photosynthesis Increases Greenhouse Gas Emissions
\item ③ The Economic Benefits of Removing Mature Trees
\item ④ How Oxygen Causes the Earth's Average Temperature to Rise
\item ⑤ The Complete Recovery of Forests Through Natural Regulation
\end{choices}

% ===================== Q4 =====================
\qno{4}\instr{[서술형] 다음 문장을 우리말로 해석하시오.}
\vspace{2pt}\par\noindent
\hspace{1em}\textit{With more carbon dioxide in the atmosphere, more of the sun's radiation is being reflected back to Earth instead of being released into space.}
\par\vspace{6pt}\noindent
$\Rightarrow$ \rule{\linewidth}{0.4pt}

\end{document}
