\documentclass[11pt,a4paper]{article}

% ===== XeLaTeX + Korean =====
\usepackage{kotex}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\setmainhangulfont{AppleMyungjo}
\setsanshangulfont{Apple SD Gothic Neo}

% ===== Layout =====
\usepackage[a4paper,top=18mm,bottom=18mm,left=20mm,right=20mm]{geometry}
\usepackage{fancyhdr}
\setlength{\headheight}{24pt}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{array}

\setlength{\parindent}{1em}
\linespread{1.18}

% ===== Header / Footer =====
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.6pt}
\fancyhead[L]{\sffamily\bfseries 2026 고1 영어 변형 — 지문 41-42}
\fancyhead[R]{\sffamily 스포츠의 예측 불가능성}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\framebox[16mm][c]{\thepage}}

% ===== helpers =====
\newcommand{\qno}[1]{\par\vspace{8pt}\noindent{\sffamily\bfseries #1.}\ }
\newcommand{\instr}[1]{{\sffamily #1}\par\vspace{3pt}}
\newlist{choices}{enumerate}{1}
\setlist[choices]{label=,leftmargin=1.5em,itemsep=2pt,topsep=3pt,parsep=0pt}

\newmdenv[linewidth=0.6pt,roundcorner=3pt,innertopmargin=7pt,innerbottommargin=7pt,
          innerleftmargin=9pt,innerrightmargin=9pt,skipabove=5pt,skipbelow=5pt]{pbox}
\newcommand{\nemo}[1]{\fbox{\,#1\,}}

\begin{document}

\begin{center}
{\fontsize{15}{17}\selectfont\sffamily\bfseries [지문 41-42] 다음 글을 읽고, 물음에 답하시오.}
\end{center}
\vspace{4pt}

% ===== 공통 지문 =====
\begin{pbox}
\hspace{1em}Commercial businesses aim for predictability and certainty, especially when it comes to product quality. But predictability and certainty are not always (a)~\underline{valued} in the sporting world, especially when it comes to the delivery of professional sport competitions. From a spectator's perspective the sport experience is better experienced when unpredictable. Sport events actually \rule{3cm}{0.4pt} that unpredictability in order to (b)~\underline{attract} people to the game. When the results of games cannot be predicted, attendances at sporting contests are likely to be higher, as are the profits of leagues. However, the (c)~\underline{presence} of predictability also leads to significant variability in the quality of sporting performances. Many factors can contribute to the variability of the sport product, including the weather, player injuries, the venue, the quality of the opponents, the closeness of the scores and even the size of the crowd. A cricket match can be exhilarating, boring or even frustrating, but fans still have to pay the same price. Sport marketers may attempt to (d)~\underline{overcome} this by `improving' the product in systematic ways, such as including a star player, offering premium seating or providing other forms of entertainment and inviting facilities. The uncertain nature of sport contests is just one element of a total experience, although it is an important element for (e)~\underline{financial} success.
\par\vspace{4pt}\footnotesize\noindent
* spectator: 관중 \quad ** venue: (스포츠 경기 등의) 장소 \quad *** exhilarating: 짜릿한
\end{pbox}

% ===================== Q1 =====================
\qno{1}\instr{윗글의 제목으로 가장 적절한 것은?}
\begin{choices}
\item ① Why Commercial Predictability Undermines Athletic Competition
\item ② The Hidden Costs of Unpredictability for Sports Marketers
\item ③ Unpredictability: The Double-Edged Sword of Sport's Appeal
\item ④ How Star Players Resolve the Problem of Uncertain Outcomes
\item ⑤ Fans and Profits: The True Measure of a Sport's Success
\end{choices}

% ===================== Q2 =====================
\qno{2}\instr{밑줄 친 (a)$\sim$(e) 중에서 문맥상 낱말의 쓰임이 적절하지 \textbf{않은} 것은? [3점]}
\begin{choices}
\item ① (a) \quad ② (b) \quad ③ (c) \quad ④ (d) \quad ⑤ (e)
\end{choices}

% ===================== Q3 =====================
\qno{3}\instr{윗글의 빈칸에 들어갈 말로 가장 적절한 것은?}
\begin{choices}
\item ① rely on
\item ② eliminate
\item ③ standardize
\item ④ ignore
\item ⑤ predict
\end{choices}

% ===================== Q4 (서술형) =====================
\qno{4}\instr{[서술형] 다음 문장을 우리말로 해석하시오.}
\vspace{4pt}\par\noindent
\hspace{1em}\textit{The uncertain nature of sport contests is just one element of a total experience, although it is an important element for financial success.}
\par\vspace{6pt}\noindent
$\Rightarrow$ \rule{\linewidth}{0.4pt}
\par\vspace{8pt}\noindent
\rule{\linewidth}{0.4pt}

\end{document}
